Source Code Volatility Metric

### 2020-04-17 paper/article.tex
cite

The metric introduced in this research belongs to the family of
``code change metrics,'' which analyze the history of changes in a repository~\citep{fentonsoftware}.
Code churn is one of the simplest metric, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}.
The number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

>>>>

The metric introduced in this research belongs to the family of
``code change metrics,'' which analyze the history of changes in a repository~\citep{fentonsoftware,choudhary2018}.
Code churn is one of the simplest metric, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}.
The number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.
